Emergence of the Southeast Asian islands as a driver for Neogene cooling

### 2020-09-10 Manuscript/Supplementary_Information.tex
update links to GitHub and Zenodo

These supplementary information materials provide details on the model framework used in this study. The code for the GEOCLIM model used in this study can be found at: \url{https://github.com/piermafrost/GEOCLIM-dynsoil-steady-state/releases/tag/v1.0}. The code that generated the inputs and analyzed the output of the GEOCLIM model can be found at: \url{https://github.com/Swanson-Hysell-Group/GEOCLIM_Modern}.

>>>>

These supplementary information materials provide details on the model framework used in this study. The code for the GEOCLIM model used in this study can be found at: \url{https://github.com/piermafrost/GEOCLIM-dynsoil-steady-state/releases/tag/v1.0}. The code that generated the inputs and analyzed the output of the GEOCLIM model can be found at: \url{https://github.com/Swanson-Hysell-Group/2020_Southeast_Asian_Islands} or \url{https://doi.org/10.5281/zenodo.4021653}.
